Beyond Ultra-Diffuse Galaxies I: Mass-Size Outliers in the Satellites of Milky Way Analogs

### 2022-10-07 paper1.tex
before moving completeness+measurement error to appendix

\subsection{Deblending}\label{sec:deblending}
Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG search \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}. A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from the real LSBGs. In order to identify and remove these objects from our sample, we perform non-parametric modeling for each object using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018}. \code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data. It utilizes the color and morphology information to separate blended objects. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.

@@

We use vanilla scarlet to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample. In the following subsections, we briefly describe our peak detection, model initialization, and measurement procedures. We refer the readers to Appendix \ref{ap:deblending} for more detailed descriptions.

@@

We notice that the optimized model of the blue LSBG captures its color and morphology quite well. For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact. The reason why it passes our initial selection is that the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and the right color. But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed.

% The models are then optimized subject to the constraints. Using the \code{scarlet} model, we extract structural and morphological parameters and use them to exclude false positives from our LSBG sample. In the following subsections, we describe our peak detection, model initialization, and measurement procedures.

{\bf Here I think belongs a paragraph with a high level summary of the steps and how they work, as above. So a few sentences on peak detection, model initialization, measurement and false positive removal. Then I'd think most of 3.2.1, 3.2.2 could go Appendix, but keeping most of the measurement stuff and visual inspection in the main text.}

\subsubsection{Peak detection}\label{sec:peak}
We generate cutout images with a size of $1\arcmin$ in the $griz$-bands for each LSBG candidate in our initial sample. We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band. This detection image is considered to be deeper than the single-band images. 
Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels. This step identifies extended sources in the detection image. However, there are still faint and compact peaks not detected. We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering in the context of LSBGs). Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels. This step detects many compact sources that were not included in the previous step. In the end, we combine the two detection catalogs.

\subsubsection{Model initialization and optimization}

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{A demonstration of the deblending step as described in Section \ref{sec:deblending}. Here we show two objects from our initial sample (Sec \ref{sec:detection}): the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts. The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay. The objects covered by the gray shades are masked. The bounding boxes and the initial models (second column) are determined from the smoothed image. The optimized models (PSF convolved) are shown in the third column, the fourth column shows the residual image, and the last column isolates the model of the target object and labels the measured color, size, and surface brightness. After such a deblending step, false positives such as the one in bottom panels can be easily removed based on their measured properties. 
	}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

\subsubsection{Measurement and false positive removal}\label{sec:non-par-measurement}

@@

After running the vanilla scarlet for LSBG candidates, we successfully deblend the target object from nearby sources. Unlike other modeling codes, the non-parametric \code{scarlet} model is very flexibly modeling galaxies with complex structures. But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model. As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we isolate the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}. The purpose of this analysis is to extract the structural and morphological parameters of the target object. We further use these diagnostics to remove false positives.

@@

We also use the Gini-M20 and CAS statistics. The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended the flux distribution is across the image. The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object. We refer the reader to \citet{statmorph} for more details on their definitions and implementations. The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.

To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the labels to construct the metrics. We randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S \ref{sec:match} for details). We run vanilla scarlet for all of them and measure morphological parameters as described above. Then we do visual inspection by looking at the $griz$ color-composite images with 0.5 arcmin on a side. Objects are classified into three types: \code{candy} (LSB galaxies with typically dwarf galaxy features), \code{galaxy} (high surface brightness galaxies, or galaxies with spiral galaxy features), and \code{junk} (false positives, including tidal streams, galaxy outskirts blends, and other artifacts). The difference between \code{candy} and \code{galaxy} can be quite ambiguous.

@@

Many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection. Among others, \citet{Tanoglidis2021} take the output catalog from \code{SourceExtractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected. \citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images. These endeavors certainly help reduce the human labor on visually inspecting tens of thousands of objects. However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space fairly evenly. Once labels are assigned (e.g., LSBG v.s. non-LSBG), there will be little way to change later. On the contrary, our cuts based on the measured properties can be tweaked to be more complete (including more junk) or be more pure (aggressive cuts) depending on the specific science goal. The visual inspection labels only guide us to design those metrics. This measurement-based method is more intuitive, reproducible, and transferable. We will also explore machine learning methods and compare with our deblending cuts in future work. We would also like to utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep{Zaritsky2021,Zaritsky2022}.

@@

\subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG sciences. Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image. Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth.

{\bf I think you can combine 3.4.1 and 3.4.2, and put most of this into the Appendix, just introduce the idea of the simulations and show the figure. I'd keep the comparison with other works in the main body of the paper.}

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$. We characterize the completeness by injecting mock \sersic{} galaxies into coadd images. The overall completeness (right panel) comprises the detection completeness (left panel, see \S \ref{sec:detection}) and deblending completeness (middle panel, see \S \ref{sec:deblending}) where false positives are removed. The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops for smaller sizes and faint surface brightness. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. The completeness drops as we go to fainter surface brightness and smaller size. 
	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
	}
	\label{fig:completeness}
\end{figure*}
\subsubsection{Completeness}\label{sec:completeness}
A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}). Thus, the overall completeness is a combination of detection completeness and deblending completeness. We performed a large suite of image simulations to derive the completeness. The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.

@@

@@

@@

However, in order to construct a UPG sample, one needs to know the distance, color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter. None of these are easy to obtain and free from systematic errors. On the one hand, reliable mass-size relation and its scatter are not available for all mass ranges. \citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$. The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color and morphology. In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$. At the same time, it is not clear whether the size distribution for a given mass can be well-described by a Gaussian distribution. Fig. 9 in \citet{ELVES-I} shows the residual in $\log(r_e)$ after fitting the mass-size relation, where the distribution of residuals is roughly Gaussian but skewed toward the large-size end. With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution. However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020} and can further benefit construct UPG samples.

@@

@@

>>>>

\subsection{Deblending}\label{sec:deblending}

\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo.pdf}
		\includegraphics[width=1\linewidth]{vanilla_scarlet_demo2.pdf}
	}
	\caption{A demonstration of the deblending step as described in \S\ref{sec:deblending}. Here we show two objects from our initial sample (\S\ref{sec:detection}): the one shown in the top panels is a blue LSBG, whereas the one shown in the bottom is a false positive detection which is a blend between high-$z$ galaxy and galaxy outskirts. The data shown in the first column is $griz$ color-composite image with the bounding boxes overlay. The objects covered by the gray shades are masked during fitting. The bounding boxes and the initial models (second column) are determined from the smoothed image. The remaining columns show the optimized models (PSF convolved), residual image, and the only target galaxy itself. 
	}
	\label{fig:vanilla_scarlet_demo}
\end{figure*}

Removing false positives from the initial sample while retaining high completeness is one of the major challenges in LSBG search \citep[e.g.,][]{vanDokkum2015,Koda2015,Yagi2016,Greco2018,SAGA-I,Zaritsky2019,Zaritsky2021,Tanoglidis2021,Zaritsky2022}. A common type of false positive occurs when point-like sources are blended with diffuse light from background galaxies or the LSB outskirts of stars and galaxies. Our initial detection cannot distinguish them from the real LSBGs. In order to identify and remove these objects from our sample, we perform non-parametric modeling using \href{https://pmelchior.github.io/scarlet/}{\code{scarlet}} \citep{Melchior2018} and design an efficient metric to remove false positives.

\subsubsection{\code{Scarlet} fitting}
\code{Scarlet} is a deblending and modeling tool designed for multi-band and multi-resolution imaging data. It utilizes the color and morphology information to separate blended objects. In the following, we briefly summarize how \code{scarlet} works, and we refer the interested readers to \citet{Melchior2018,Melchior2021} and the online documentation\footnote{\url{https://pmelchior.github.io/scarlet/}} for more details.

@@

We use vanilla scarlet to model the LSBG candidate and extract structural and morphological parameters from the \code{scarlet} model, which are further used to exclude false positives from our LSBG sample. In the following subsections, we briefly describe how we detect peaks on the image, initialize and optimize \code{scarlet} models. We refer the readers to Appendix \ref{ap:deblending} for more detailed descriptions.

@@

We notice that the optimized model of the blue LSBG captures its color and morphology quite well. For the false-positive case, the optimized model has a notable bright background thanks to the flat-sky component, and the model for the target itself is very red and compact. The reason why it passes our initial selection is that the galaxy outskirts are shredded by \code{SourceExtractor} and happen to have a large size and the right color. But once modeled using \code{scarlet}, it becomes clear that this is just a false positive detection and should be removed. A rubric based on the \code{scarlet} model is therefore needed to help us exclude the false positives.

% {\bf Here I think belongs a paragraph with a high level summary of the steps and how they work, as above. So a few sentences on peak detection, model initialization, measurement and false positive removal. Then I'd think most of 3.2.1, 3.2.2 could go Appendix, but keeping most of the measurement stuff and visual inspection in the main text.}

\subsubsection{False positive removal}\label{sec:non-par-measurement}

@@

After running the vanilla scarlet for LSBG candidates, we successfully deblend the target object from nearby sources. Unlike other parametric modeling methods, the non-parametric \code{scarlet} model is very flexible on modeling galaxies with complex structures. But the non-parametric nature of the code means that we have to make our own measurements to quantify the size and shape of the \code{scarlet} model. As shown in the last column of Figure \ref{fig:vanilla_scarlet_demo}, we isolate the model of the target object and analyze it using \href{https://statmorph.readthedocs.io/en/latest/}{\code{statmorph}} \citep{statmorph}. The purpose of this analysis is to extract the structural and morphological parameters of the target object. We further use these diagnostics to remove false positives.

@@

We also use the Gini-M20 and CAS statistics. The Gini coefficient and M20 statistics \citep{Abraham2003,Lotz2004} quantify how concentrated/extended the flux distribution is across the image. The CAS statistics characterize the concentration $C$, asymmetry $A$, and smoothness $S$ of the light distribution of the object. We refer the reader to \citet{statmorph} for more details on their definitions and implementations. We measure the morphological and structural parameters in $g$-band. %The morphological and structural parameters are the same in different bands by construction in the \code{scarlet} model.

To better guide us on how to use these diagnostics, we visually inspect a subset of LSBG candidates in our initial sample (\S \ref{sec:detection}) and use the labels to construct the metrics. To be specific, we randomly selected 5,000 LSBG candidates that are matched with a MW-like host at $0.01 < z < 0.04$ in NSA catalog (see \S\ref{sec:match} for details). We run vanilla scarlet for all of them and measure morphological parameters as described above. Then we do visual inspection by looking at the $griz$ color-composite images with 0.5 arcmin on a side. Objects are classified into three types: LSB galaxies with typically dwarf galaxy features (dubbed \code{candy}), high surface brightness galaxies, or galaxies with spiral galaxy features (\code{galaxy}), and false positives including tidal streams, galaxy outskirts blends, and other artifacts (\code{junk}). The difference between \code{candy} and \code{galaxy} can be quite ambiguous.

@@

Many other works have been using machine learning (ML) algorithms to classify LSBG candidates and exclude spurious detection. Among others, \citet{Tanoglidis2021} take the output catalog from \code{SourceExtractor} and use the Support Vector Machine algorithm to classify objects in their initial sample and reduce the number of objects that are visually inspected. \citet{Zaritsky2019,Zaritsky2021,Zaritsky2022} use convolutional neural networks to classify LSBGs into binary classes based on their images. These endeavors certainly help reduce the human labor on visually inspecting tens of thousands of objects. However, training such a supervised ML algorithm relies on the labeled data which should also sample the parameter space fairly evenly. Once labels are assigned (e.g., LSBG v.s. non-LSBG), there will be little way to change later. On the contrary, our cuts based on the measured properties can be tweaked to have higher completeness  (including more junk) or have higher purity (aggressive cuts) depending on the specific science goal. The visual inspection labels only guide us to design those metrics. This measurement-based method is more intuitive, reproducible, and transferable. We will also explore machine learning methods and compare with our deblending cuts in future works. We would also like to utilize information about Milky Way dust to exclude spurious detection on Galactic cirrus \citep[e.g.,][]{Zaritsky2021,Zaritsky2022}.

@@

\subsection{Completeness and Measurement Uncertainty}\label{sec:comp_meas}
\begin{figure*}
	\vbox{ 
		%\vskip -10mm
		\centering
		\includegraphics[width=1\linewidth]{completeness.pdf}
	}
	\caption{The completeness of our LSBG search as a function of effective radius $r_e$ and the average surface brightness $\sbeff$. We characterize the completeness by injecting mock \sersic{} galaxies into coadd images. The overall completeness (right panel) comprises the detection completeness (left panel, see \S \ref{sec:detection}) and deblending completeness (middle panel, see \S \ref{sec:deblending}) where false positives are removed. The dashed lines in the right panel highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops for smaller sizes and faint surface brightness. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. The completeness drops as we go to fainter surface brightness and smaller size. 
	%The mock galaxies span a large range in size, surface brightness, \sersic{} index, color, and ellipticity. 
	}
	\label{fig:completeness}
\end{figure*}

The completeness of the LSBG search is important not only for understanding our search efficiency and improving the method in the future, but also for deriving the completeness-corrected results for LSBG sciences. Similar to many other works \citep[e.g.,][]{vdBurg2017,Zaritsky2021,CarlstenELVES2022,Greene2022}, we derive the completeness by simulating mock LSBGs and recovering them from the image. Using these mock galaxies, we also characterize the measurement bias and uncertainty by comparing the measured properties with the truth. We present the main steps below and describe details in Appendix \ref{ap:comp_meas_unc}.

A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}). Thus, the overall completeness is a combination of detection completeness and deblending completeness. We performed a large suite of image simulations to derive the completeness. We inject single \sersic{} light profile \citep{Sersic1963} to the coadd images and try do recover them using the detection method (\S\ref{sec:detection}), model them using vanilla \code{scarlet} (\S\ref{sec:deblending}), and apply the deblending cuts. The mock \sersic{} galaxies span a wide range in size ($2\arcsec \leqslant r_{e} \leqslant 21\arcsec$) and surface brightness ($23 \leqslant \overline{\mu}_{\rm eff}(g) \leqslant 28.5\ \mathrm{mag\ arcsec^{-2}}$). The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.

We find that the completeness mainly depends on the size and surface brightness. As shown in Figure \ref{fig:completeness}, the detection completeness remains high across different sizes. It drops below 50\% when the surface brightness gets fainter than $\sbeff = 27.5\ \sbunit$. The deblending completeness is very high at the bright end, but starts to decline with increasing size and decreasing surface brightness. Mock galaxies fainter than $\sbeff > 27.5\ \sbunit$ are mostly removed by the deblending step, likely due to the blending of other small compact sources with the mock galaxy. Interestingly, the detection completeness and deblending completeness all drop below 40\% around $\sbeff=27.5\ \sbunit$. In this sense, the detection and deblending cooperate well in terms of completeness.

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops as we go to fainter surface brightness and smaller size. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness. In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).

The size, magnitude, surface brightness, and shape of LSBGs are hard to characterize because of the low surface brightness nature. 
\citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects. In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties. Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs. \citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth. \citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network. In this paper, we simply take the former method because of its simplicity.

We perform the Spergel profile modeling (as described in \S\ref{sec:modeling}) for the mock \sersic{} galaxies and compare the modeling results with the ground truth. We find that the measured effective radius $r_e$ is biased to be smaller than the truth, and the bias depends on the surface brightness and the angular size. For surface brightnesses fainter than $27\ \sbunit$, the measured size can be much smaller than the truth. As a result, the total magnitude $m$ and the average surface brightness $\overline{\mu}_{\rm eff}$ are also measured to be fainter than reality. Similar to \citet{Zaritsky2021}, we derive the measurement biases and uncertainties in size, surface brightness, total magnitude, and color as a function of size and surface brightness. We refer interested readers to Appendix \ref{ap:comp_meas_unc} for details. The main results are shown in Figure \ref{fig:meas_err}, where the colors show the bias terms as a function of the measured size and surface brightness. The size and surface brightness bias grows with increasing surface brightness. The bias term is not a monotonic function of size because the size here is not intrinsic size. It is the bias in size measurement that makes galaxies with large intrinsic $r_e$ pile up around $r_e\sim 6\arcsec$. We also find the bias in $g-i$ color to be quite small. The measurement errors $\sigma(X)$ are shown in Figure \ref{fig:meas_err} as contours, and they have the same units as the biases. We set minimum uncertainties to be $\sigma(r_e) \geqslant 0.3,\ \sigma(\overline{\mu}_{\rm eff}) \geqslant 0.05,\ \sigma(g-i) \geqslant 0.05$ to avoid meaningless uncertainty due to small statistics.

% {\bf I think you can combine 3.4.1 and 3.4.2, and put most of this into the Appendix, just introduce the idea of the simulations and show the figure. I'd keep the comparison with other works in the main body of the paper.}

\subsubsection{Completeness}\label{sec:completeness}
A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}). Thus, the overall completeness is a combination of detection completeness and deblending completeness. We performed a large suite of image simulations to derive the completeness. The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.

@@

The combined completeness is shown in the right panel of Figure \ref{fig:completeness}. The dashed lines highlight the 70\%, 50\%, and 20\% completeness contours. The completeness drops as we go to fainter surface brightness and smaller size. We are $>70\%$ complete to $\sbeff < 26.5\ \sbunit$ and $3\arcsec < r_e < 14\arcsec$, and $>50\%$ complete to $\sbeff \leqslant 27.0\ \sbunit$. Although \sersic{} galaxies do not necessarily resemble the morphology of real LSBGs, our completeness based on \sersic{} model still sets a baseline or upper limit on the real completeness. In the future, we might be more capable of generating realistic LSBGs using deep learning techniques (e.g., diffusion model).

@@

Due to the low surface brightness nature of LSBGs, their size, magnitude, surface brightness, and shape are hard to characterize and are typically associated with large uncertainties. \citet{Haussler2007} use mock single-\sersic{} galaxies and parametric fitting codes to demonstrate that the estimated size and total magnitude are sensitive to local sky estimation and masking of neighboring objects. In the low surface brightness regime, the measured size and total magnitude can be quite biased and have large uncertainties. Therefore, measurement bias and uncertainty must be considered when studying the properties of LSBGs. \citet{Zaritsky2021,Zaritsky2022} characterize their measurement bias and uncertainty by injecting mock \sersic{} galaxies into the coadd and compare the recovered properties with the truth. \citet{Tanoglidis2022ICML} recently propose a new method to estimate the measurement error using a Bayesian Neural Network. In this paper, we simply take the former method because of its simplicity.

@@

However, in order to construct a UPG sample, one needs to know the distance, color, a color-$M_\star/L$ relation to convert observed magnitudes to stellar mass, and a mass-size relation and its scatter. None of these are easy to obtain and free from systematic errors. On the one hand, reliable mass-size relation and its scatter are not available for all mass ranges. \citet{ELVES-I} derive the mass-size relation below $M_\star \sim 10^{8.5}\ M_\odot$, whereas \citet{Lange2015} have relatively good constraints on the mass-size relation only above $M_\star \sim 10^{9}\ M_\odot$. The mass-size relation at $10^{8.5}\ M_\odot < M_\star < 10^{9}\ M_\odot$ is not well measured, nor is any dependence on color and morphology. In this work, we simply extrapolate the \citet{ELVES-I} mass-size relation to $10^9\ M_\odot$. At the same time, it is not clear whether the size distribution for a given mass can be well-described by a Gaussian distribution. Fig. 9 in \citet{ELVES-I} shows the residual in $\log(r_e)$ after fitting the mass-size relation, where the distribution of residuals is roughly Gaussian but skewed toward the large-size end. With enough statistics in the future, one might be able to characterize the shape of the large-size tail and define UPGs based on the percentiles of the size distribution. However, there are also other size definitions which help to reduce the scatter in the mass-size relation \citep[e.g.,][]{Miller2019,Mowla2019,Trujillo2020,Chamba2022} and can further benefit construct UPG samples.

@@

\subsection{Peak detection}\label{sec:peak}
We generate cutout images with a size of $1\arcmin$ in the $griz$-bands for each LSBG candidate in our initial sample. We then construct a detection image by taking an average of the four bands weighted by the inverse variance of each band. This detection image is considered to be deeper than the single-band images. 
Next, we run \code{sep} on the detection image using a threshold of 4$\sigma$ above the sky, a mesh size of 48 pixels ($8\arcsec$), and a kernel size of 3 pixels. This step identifies extended sources in the detection image. However, there are still faint and compact peaks not detected. We apply a wavelet decomposition to the detection image \citep{Starck2015} and only keep the high spatial frequency components (also see \citealt{Zaritsky2019} for an example of using wavelet filtering in the context of LSBGs). Another round of \code{sep} is run on this high-frequency image using a detection threshold of 2.5$\sigma$, a mesh size of 24 pixels, and a kernel size of 3 pixels. This step detects many compact sources that were not included in the previous step. In the end, we combine the two detection catalogs and remove duplicates.

\subsection{Model initialization and optimization}

@@

\section{Completeness and Measurement Uncertainty}\label{ap:comp_meas_unc}
A real LSBG can be missed in the detection step (\S \ref{sec:detection}) or be excluded in the deblending step (\S \ref{sec:deblending}). Thus, the overall completeness is a combination of detection completeness and deblending completeness. We performed a large suite of image simulations to derive the completeness. The detection completeness is defined as the number of detected objects divided by the number of injected objects, whereas the deblending completeness is defined as the fraction of objects remaining after the deblending cuts.
